draft

### 2021-05-16 code/draft.Rmd
Add prevalence graph

## Preparation
1. Setup
```{r setup, message=FALSE, warning=FALSE}
# Loading library here
library(knitr)
library(tidyverse)
library(readxl)
library(ggrepel)
library(rstatix)

@@

@@

>>>>

## Preparation
1. Setup
```{r setup, message=FALSE, warning=FALSE}
# Loading library here
library(knitr)
library(tidyverse)
library(readxl)
library(ggrepel)
library(rstatix)
library(ggpubr)
library(epitools)

@@

BW_f_3_w15 <- BW_f_3 %>% filter(TimePoint_Weeks==15) %>% group_by(Sex) %>% pairwise_t_test(Weight_g ~ BirthMode, p.adjust.method = "fdr") %>% add_y_position(step.increase = 0.05) %>% p_format(p.adj, leading.zero = FALSE, accuracy = 0.001)

ggplot(BW_f_3 %>% filter(TimePoint_Weeks==15), aes(x = BirthMode, y = Weight_g)) +
    geom_boxplot(outlier.shape = NA, width = 0.5) +
    geom_beeswarm(aes(color = BirthMode), cex = 2.5, show.legend = F) +
    stat_pvalue_manual(BW_f_3_w15, label = "p.adj", tip.length = 0.01, hide.ns = T) +
    facet_grid(.~Sex) +
    theme_jw(base_size = 14) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual(values = BM_colors) +
    labs(x = "Birth Mode", y = "Body Weight (g)", subtitle = "Pairwise t-test with FDR adjustments did not reveal any statistical significance")

BW_f_3_ow <- BW_f_3 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(Pct_over = sum(Flag=="Overweight")/n())
BW_f_3_ow_stats_dat <- BW_f_3 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(N_sub = n(), N_over = sum(Flag=="Overweight"), N_under = sum(Flag=="Underweight"))
BW_f_3_ow_stats <- BW_f_3_ow_stats_dat %>% arrange(Sex, TimePoint_Weeks, BirthMode) %>% ungroup %>% split(., list(.$Sex, .$TimePoint_Weeks)) %>% lapply(., function(y){y %>% mutate(N_normal = N_sub - N_over - N_under) %>% select(BirthMode, N_normal, N_over) %>% column_to_rownames(var = "BirthMode") %>% as.matrix() %>% oddsratio.fisher()}) %>% lapply(., function(x){merge(merge(as.data.frame(x$data)[1:4, 1:2], as.data.frame(x$measure), by = 0), as.data.frame(x$p.value)[2], by.x = 1, by.y = 0)}) %>% data.table::rbindlist(idcol = "Sex.Weeks") %>% separate(Sex.Weeks, into = c("Sex", "TimePoint_Weeks"), sep = "\\.") %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))

BW_f_3_ow_ = full_join(BW_f_3_ow, BW_f_3_ow_stats, by = c("Sex" = "Sex", "TimePoint_Weeks"="TimePoint_Weeks", "BirthMode"="Row.names")) %>% mutate(q.fdr = p.adjust(fisher.exact, method = "fdr"), sig = case_when(q.fdr<=0.001 ~ "***", q.fdr<=0.01 ~ "**", q.fdr <=0.05 ~ "*", T ~ NA_character_))

ggplot(BW_f_3_ow_, aes(x = TimePoint_Weeks, y = Pct_over, color = BirthMode)) +
    geom_point(size = 2) +
    geom_line(size = 1) +
    geom_text(aes(label = sig), na.rm = T,  nudge_y = 0.05, show.legend = F) + 
    annotate("segment", x=-Inf, xend = Inf, y = -Inf, yend = -Inf) +
    facet_wrap(.~Sex, ncol = 1) +
    scale_color_manual(values = BM_colors) +
    scale_x_continuous(breaks = seq(4,15,2)) +
    scale_y_continuous(breaks = seq(0,0.8, 0.2)) +
    theme_jw(base_size = 14) + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank()) +
    labs(x = "Weeks", y = "Prevalence of overweight")

@@

BW_f_4_w15 <- BW_f_4 %>% filter(TimePoint_Weeks==15) %>% group_by(Sex) %>% pairwise_t_test(Weight_g ~ BirthMode, p.adjust.method = "fdr") %>% add_y_position(step.increase = 0.05) %>% p_format(p.adj, leading.zero = FALSE, accuracy = 0.001)

ggplot(BW_f_4 %>% filter(TimePoint_Weeks==15), aes(x = BirthMode, y = Weight_gain)) +
    geom_boxplot(outlier.shape = NA, width = 0.5) +
    geom_beeswarm(aes(color = BirthMode), cex = 2.5, show.legend = F) +
    stat_pvalue_manual(BW_f_3_w15, label = "p.adj", tip.length = 0.01, hide.ns = T) +
    facet_grid(.~Sex) +
    theme_jw(base_size = 14) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual(values = BM_colors) +
    labs(x = "Birth Mode", y = "Body Weight gain(% to week 3 body weight)", subtitle = "Pairwise t-test with FDR adjustments did not reveal any statistical significance")

BW_f_4_ow <- BW_f_4 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(Pct_over = sum(Flag=="Overweight")/n())
BW_f_4_ow_stats_dat <- BW_f_4 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(N_sub = n(), N_over = sum(Flag=="Overweight"), N_under = sum(Flag=="Underweight"))
BW_f_4_ow_stats <- BW_f_4_ow_stats_dat %>% arrange(Sex, TimePoint_Weeks, BirthMode) %>% ungroup %>% split(., list(.$Sex, .$TimePoint_Weeks)) %>% lapply(., function(y){y %>% mutate(N_normal = N_sub - N_over - N_under) %>% select(BirthMode, N_normal, N_over) %>% column_to_rownames(var = "BirthMode") %>% as.matrix() %>% oddsratio.fisher()}) %>% lapply(., function(x){merge(merge(as.data.frame(x$data)[1:4, 1:2], as.data.frame(x$measure), by = 0), as.data.frame(x$p.value)[2], by.x = 1, by.y = 0)}) %>% data.table::rbindlist(idcol = "Sex.Weeks") %>% separate(Sex.Weeks, into = c("Sex", "TimePoint_Weeks"), sep = "\\.") %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))

BW_f_4_ow_ = full_join(BW_f_4_ow, BW_f_4_ow_stats, by = c("Sex" = "Sex", "TimePoint_Weeks"="TimePoint_Weeks", "BirthMode"="Row.names")) %>% mutate(q.fdr = p.adjust(fisher.exact, method = "fdr"), sig = case_when(q.fdr<=0.001 ~ "***", q.fdr<=0.01 ~ "**", q.fdr <=0.05 ~ "*", T ~ NA_character_))

ggplot(BW_f_4_ow_, aes(x = TimePoint_Weeks, y = Pct_over, color = BirthMode)) +
    geom_point(size = 2) +
    geom_line(size = 1) +
    geom_text(aes(label = sig), na.rm = T,  nudge_y = 0.05, show.legend = F) + 
    annotate("segment", x=-Inf, xend = Inf, y = -Inf, yend = -Inf) +
    facet_wrap(.~Sex, ncol = 1) +
    scale_color_manual(values = BM_colors) +
    scale_x_continuous(breaks = seq(4,15,2)) +
    scale_y_continuous(breaks = seq(0,0.8, 0.2)) +
    theme_jw(base_size = 14) + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank()) +
    labs(x = "Weeks", y = "Prevalence of overweight")
